% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{kpfonts} 
\usepackage[T1]{fontenc} 
\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\vspace{10mm}

\name{David Gibb}
% \address used twice to have two lines of address
\address{350 Pierce Street, San Francisco, CA}
\address{cell: (415) 967-1235 email: degibb@gmail.com}

 
\begin{resume}
\section{OBJECTIVE}       A position in the field of information technology, with special 
                interests in business applications programming, semantic standards-based web applications,
                information processing, and management systems. 
 
%\section{OBJECTIVE}    A position in the field of data processing and
%mathematical modeling, with an emphasis on stochastic models. 


\section{EXPERIENCE} 
{\sl Solutions Architect} \hfill March 2011 - \\
                AurionPro Solutions, 
                San Francisco, USA
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Served as Technical Lead for a high traffic commercial
                   intranet migration. Recommended, designed, and implemented a
                   replacement for a legacy system which improved authoring
                   experience and performance, and saved over \$300k/year in
                   licensing fees.
                 \item Led the migration of a major public facing technology
                 site to Drupal 7, easing content management and adding new
                 emphasis on the client's core strengths. The resulting
                 SEO and content entry improvements led to
                 pageviews increasing by \%78, visits up \%66.
                 \item Improved reliability and deployment timeframe of a
                 complex process management application through the introduction
                 of systematic acceptance testing. Dramatically increased
                 performance by adapting and tuning the persistence layer.
                 \item Led the rich user experience redesign of a medical
                 service portal. Was responsible for implementing high level
                 composites as well as designing dynamic front-end behaviour
                 for a modern user experience.
                 \end{itemize}
                    
{\sl Web Development Engineer} \hfill May 2010 - August 2010\\
                TP1 Internet 360, 
                Montreal, Canada
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed complex rules-based translation system for a
                 multilingual content-heavy site.
                 \item Implemented a customized e-commerce solution with a
                 Drupal CMS front end and a customized Magento backend.
                 \end{itemize}

{\sl Web Development Engineer} \hfill May 2009 - April 2010\\
                EvolvingWeb, 
                Montreal, Canada
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Developed rich user experiences using Drupal in
                 combination with third party interfaces such as video and
                 mapping services.
                 \item Implemented lucene/solr search, integrated with AJAX
                 callback and geolocation interface.
                 \item Developed automated testing procedures using the
                 Selenium web testing framework and the Hudson continuous
                 integration server.
                 \end{itemize}
                
{\sl Senior Consultant} \hfill May 2006 - August 2008\\
                Vignette Corporation, 
                Paris, France
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Implemented customized collaborative and portal solutions for major governmental and private organizations using Vignette Portal and Vignette Collaboration. Integrated these products with a variety of legacy systems. 
                \item Developed long-term relationships with clients and partners by providing a high level of support and transparency.
                \item Designed, implemented, and supported custom solutions for
                a wide variety of requirements and user bases. 
				\item Assisted in the sales process by developing extensive custom proof of concept demonstrations for the Vignette sales team under tight time constraints.
                \end{itemize}
                                    
\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} 
	\begin{itemize}
    \item Experienced in a wide variety of data processing tasks using matlab,
      maple, python tools, R, etc. Includes experience creating custom monte-carlo
      type models.
    \item Proficient in modern front-end engineering techniques, including
      structured Javascript techniques (IIFE, modules, etc). Many years of 
      experience using jQuery, familiar with tools such as BackboneJS and
      Jasmine.
    \item Advocate for design implementation tools such as SASS and
      Compass, and techniques such as Responsive design.
    \item Proven experience performance tuning using a combination of
      techniques such as compression, reverse-proxying, object and fragment caching, and
      HTTP header manipulation.
		\item Familiar in a wide variety of programming languages such as Java, Python, Scheme, PHP, and paradigms including Object Oriented, Functional, and Data Directed. 
    \item Extensive background in web content management, including licensed
      enterprise solutions like Vignette and open source
      solutions like Drupal.
    \item Excellent knowledge of MVC frameworks such as Spring, with a special
      interest in modern lightweight alternatives such as Django and Rails.
		\item Experienced in REST service oriented architecture. More sophisticated
      implementations of REST involving concurrency and complicated business
      logic are a specialty.
    \item Proficient in relational database theory, as well as working knowledge of all major
      RDBMS vendors. Familiar with NoSQL implementations such as MongoDB, as
      well as map-reduce theory.
		\item Skilled system administrator on Linux, Unix and Windows platforms        
		\item Extensive use of VMWare and Virtualbox virtualization technologies for prototyping,
    and development. Experienced using Vagrant and Chef for rapid provisioning
    and testing.
	\end{itemize}
      {\sl Project Management:}
	\begin{itemize}
		\item Agile project management evangelist, with expertise in
        implementing Scrum and XP.
		\item Proven track record implementing tools designed to improve code
        quality and reduce time to deliverables, such as source control
        management, unit and functional testing, and continuous integration
        servers.        
	\end{itemize}
                 
\section{EDUCATION} {\sl Bachelor of Science,} Major in Mathematics \\
                McGill University, Montreal, QC,  \\
                Minor: Physics 
 
			{\sl Secondary/International Baccalaureate Diploma,} \\
                Jakarta International School,
                Jakarta, Indonesia,  \\
                Achieved highest score in International Baccalaureate Mathematics, Physics, and Computer Science examinations
                
\section{OTHER \\ SKILLS \& CERTIFICATIONS}             
Fluent in spoken French. Excellent written French. \\
Enthusiastic tennis player and cyclist. \\
Amateur machinist and welder.

\end{resume}
\end{document}







